Theory about Normal Basis on $F(2^k)$

### 2016-12-11 dissertation/appendix.tex
dissertation v3:milestone

Let $k$ be a polynomial whose degree is larger than $f(x)$, i.e. $deg(k(x))>deg(f(x))$, then
$$f(x)|k(x)~~\text{iff}~k(T)=0$$

@@

Use Lemma \ref{lem:3}, the minimal/characteristic polynomial for $\sigma$ is $x^n-1$ implies that
any annihilator of $\alpha^i$ ({\it i.e.} $f_i(\sigma)$) divides $x^n-1$. Meanwhile, $\{\alpha^i~|~0<i<n-1\}$ forms a (standard) basis
of field $\F_{p^n}$, this means $\alpha_i$ are linearly independent with each other ($i=0,1,\dots,n-1$).
Since linear map $f(\sigma)$ guarantees that all elements in the field 
have order $lcm(f_0,\dots,f_{n-1})$, i.e. $f(\sigma)\gamma = f(\sigma)(\sum_i \alpha^i) \implies f(\sigma) = lcm(f_0,\dots,f_{n-1})$.
By contradiction we can prove that there is no factor of $x^n-1$ that can be divided by the product 
of elements in set $\{f_0,f_1,\dots,f_{n-1}\}$. This actually corresponds to the assertion in the first step of the algorithm:
$$x^n-1 = lcm(f_0,f_1,\dots,f_{n-1})$$

@@

\section{Optimal Normal Basis}
\label{append:ONB}
The number of non-zero entries in $\lambda$-Matrix or multiplication table (M-table) is known as \emph{Complexity $(C_N)$}.
To define optimal normal basis, it is necessary to find the lower bound of $C_N$.
\begin{Theorem}
If N is a normal basis over $\F_{p^n}$ with $\lambda$-Matrix $M^{(k)}$, then non-zero entries in matrix $C_N\geq 2n-1$.
\end{Theorem}
\begin{Proof}
Let basis $N = \{\beta, \beta^p, \beta^{p^2},\dots, \beta^{p^{n-1}}\}$, let us denote $\beta^{p^i}$ by $\beta_i$ for the sake of simplification.
Then $\sum_{i=0}^{n-1} \beta_i = trace\ \beta$. 
Denote $trace\ \beta$ by $b$, consider a $n\times n$ matrix $M^{(0)}$. Then
$$b\beta_0 = \sum_{i=0}^{n-1} \beta \beta_i$$

Therefore, the sum of all rows in $M^{(0)}$ is an n-tuple with $b$ as the first element and zeros elsewhere.
So the first column always includes at least one nonzero element. 
Since the sum of enries in each of other columns should equal to zero (modulo 2), they 
need to include an even number of ``1"s.
Meanwhile, in order to maintain the linear independence among each row, they cannot be all ``0"s. 
Therefore, there are always at least two non-zero elements in each column.

@@

\begin{Example}
\label{ex:app4}
In $\F_{2^4}$ constructed with $p(\alpha) = \alpha^4 + \alpha + 1$, two normal bases can be found:
$\beta = \alpha^3, N_1 = \{ \alpha^3, \alpha^6, \alpha^{12}, \alpha^9\}$ and 
$\beta = \alpha^7, N_2 = \{\alpha^7, \alpha^{14}, \alpha^{13}, \alpha^{11}\}$. 
Their multiplication tables are listed below. For basis $N_1$:
\begin{equation}
T_1 = \left(
\begin{array}{lccr}
0 & 1 & 0 & 0\\
0 & 0 & 0 & 1\\
1 & 1 & 1 & 1\\
0 & 0 & 1 & 0
\end{array} \right)
\end{equation}
Complexity $C_N$ = 7, so $N_1$ is an ONB. For basis $N_2$:
\begin{equation}
T_2 = \left(
\begin{array}{lccr}
0 & 1 & 0 & 0\\
1 & 1 & 0 & 1\\
1 & 0 & 1 & 0\\
1 & 0 & 1 & 1
\end{array} \right)
\end{equation}
Complexity $C_N$ = 9, so basis $N_2$ is not optimal.
\end{Example}

@@

Solution $(i,j)$ implies location of entries that equal to ``1" in $\lambda$-Matrix. 
Let $\beta$ be an optimal normal element, 
$\{\beta^{2^i}~|~0\leq i<n\}$ cover all powers of $\beta$ and generates the basis. Thus by solving
$$\begin{cases}
2^i + 2^j = 1 \pmod{n+1}\\
2^i + 2^j = 0 \pmod{n+1}
\end{cases}$$
we obtain $\lambda$-Matrix $M^{(0)}$. This construction method does not require information about 
primitive polynomial nor normal element, so it is very convenient for circuit designers.
Basis $N_1$ in Example \ref{ex:app4} is a type-I ONB over $\F_{2^4}$.

>>>>

Let $k$ be a polynomial whose degree is larger than $f(x)$, {\it i.e.} $deg(k(x))>deg(f(x))$, then
$$f(x)|k(x)~~\text{iff}~k(T)=0$$

@@

Use Lemma \ref{lem:3}, the minimal/characteristic polynomial for $\sigma$ is $x^n-1$ implies that
any annihilator of $\alpha^i$ ({\it i.e.} $f_i(\sigma)$) divides $x^n-1$. Meanwhile, $\{\alpha^i~|~0<i<n-1\}$ forms a (standard) basis
of field $\F_{p^n}$, this means $\alpha_i$ are linearly independent with each other ($i=0,1,\dots,n-1$).
Since linear map $f(\sigma)$ guarantees that all elements in the field 
have order $lcm(f_0,\dots,f_{n-1})$, {\it i.e.} $f(\sigma)\gamma = f(\sigma)(\sum_i \alpha^i) \implies f(\sigma) = lcm(f_0,\dots,f_{n-1})$.
By contradiction we can prove that there is no factor of $x^n-1$ that can be divided by the product 
of elements in set $\{f_0,f_1,\dots,f_{n-1}\}$. This actually corresponds to the assertion in the first step of the algorithm:
$$x^n-1 = lcm(f_0,f_1,\dots,f_{n-1})$$

@@

\section{Optimal Normal Basis}
\label{append:ONB}
The number of non-zero entries in $\lambda$-Matrix or multiplication table (M-table) is known as \emph{Complexity $(C_N)$}.
To define optimal normal basis, it is necessary to find the lower bound of $C_N$.
\begin{Theorem}
If $\mathcal{N}$ is a normal basis over $\F_{p^n}$ with $\lambda$-Matrix $M^{(k)}$, then non-zero entries in matrix $C_N\geq 2n-1$.
\end{Theorem}
\begin{Proof}
Let basis $\mathcal{N} = \{\beta, \beta^p, \beta^{p^2},\dots, \beta^{p^{n-1}}\}$, let us denote $\beta^{p^i}$ by $\beta_i$ for the sake of simplification.
Then $\sum_{i=0}^{n-1} \beta_i = trace\ \beta$. 
Denote $trace\ \beta$ by $b$, consider a $n\times n$ matrix $M^{(0)}$. Then
$$b\beta_0 = \sum_{i=0}^{n-1} \beta \beta_i$$

Therefore, the sum of all rows in $M^{(0)}$ is an n-tuple with $b$ as the first element and zeros elsewhere.
So the first column always includes at least one nonzero element. 
Since the sum of entries in each of other columns should equal to zero (modulo 2), they 
need to include an even number of ``1"s.
Meanwhile, in order to maintain the linear independence among each row, they cannot be all ``0"s. 
Therefore, there are always at least two non-zero elements in each column.

@@

\begin{Example}
\label{ex:app4}
In $\F_{2^4}$ constructed with $p(\alpha) = \alpha^4 + \alpha + 1$, two normal bases can be found:
$\beta = \alpha^3, \mathcal N_1 = \{ \alpha^3, \alpha^6, \alpha^{12}, \alpha^9\}$ and 
$\beta = \alpha^7, \mathcal N_2 = \{\alpha^7, \alpha^{14}, \alpha^{13}, \alpha^{11}\}$. 
Their multiplication tables are listed below. For basis $\mathcal N_1$:
\begin{equation}
T_1 = \left(
\begin{array}{lccr}
0 & 1 & 0 & 0\\
0 & 0 & 0 & 1\\
1 & 1 & 1 & 1\\
0 & 0 & 1 & 0
\end{array} \right)
\end{equation}
Complexity $C_N$ = 7, so $\mathcal N_1$ is an ONB. For basis $\mathcal N_2$:
\begin{equation}
T_2 = \left(
\begin{array}{lccr}
0 & 1 & 0 & 0\\
1 & 1 & 0 & 1\\
1 & 0 & 1 & 0\\
1 & 0 & 1 & 1
\end{array} \right)
\end{equation}
Complexity $C_N$ = 9, so basis $\mathcal N_2$ is not optimal.
\end{Example}

@@

Solution $(i,j)$ implies location of entries that equal to ``1" in $\lambda$-Matrix. 
Let $\beta$ be an optimal normal element, 
$\{\beta^{2^i}~|~0\leq i<n\}$ cover all powers of $\beta$ and generates the basis. Thus by solving
$$\begin{cases}
2^i + 2^j = 1 \pmod{n+1}\\
2^i + 2^j = 0 \pmod{n+1}
\end{cases}$$
we obtain $\lambda$-Matrix $M^{(0)}$. This construction method does not require information about 
primitive polynomial nor normal element, so it is very convenient for circuit designers.
Basis $\mathcal N_1$ in Example \ref{ex:app4} is a type-I ONB over $\F_{2^4}$.

### 2016-12-11 dissertation/conclude.tex
dissertation v3:milestone

\section{Future Work}
In this section, we highlight some research problems that deserve further study.
\subsection{Multivariate polynomial ideal based FSM traversal}
In Chapter \ref{ch:reacha}, we always use a single word-level variable $T$ to denote the
next state. However, in some situations we need to keep recording the relations between $T$ and
inputs, {\it i.e.} the reached states contain multivariate polynomials in $T,S$ and PI $x$. 
While the elimination and set union/intersection are compatible with multiple NS variables,
the set complement requires an extension of Theorem \ref{thm:quotient} on ideals with 
multivariate polynomial generators. We conjecture as follows:

@@

\subsection{Use of the $F_4$ algorithm and ZDDs to Accelerate GB Reduction}
In Chapters \ref{ch:reacha} and \ref{ch:normal}, by using RATO we transform the GB-based
computation to that of a multivariate polynomial division. However, this division (reduction)
still incurs exponential complexity in the worst case. In a situation where division is to be performed modulo
a chain of OR gates, the size of remainder polynomial will explode. For example, a chain of OR gates 
can be written as the Boolean function 
\begin{equation}
\label{eqn:chainOR}
f = ((a\lor b) \lor c) \lor d
\end{equation}
which equals to the following polynomial function in $\F_2$:
$$f = abcd+abc+abd+ab+acd+ac+ad+a+bcd+bc+bd+b+cd+c+d$$
Notice, $f$ contains $2^4-1 = 15$ terms, which is exponential in the number of variables.
The size explosion is a major factor affecting the efficiency of polynomial division.

@@

\begin{Definition}
(From \cite{mcmillan2003interpolation}) Let $A$ and $B$ be Boolean
  formulae given as sets of clauses such that $A \wedge B$ is
  unsatisfiable (UNSAT). Then there exists a formula $P$ such that: 
1) $A$ implies $P$ (or $A \subseteq P$); ~2) $P \wedge B$ is UNSAT; ~3)
$P$ refers to only the common variables of $A$ and $B$. The formula
$P$ represents an {\bf interpolant} of $A$ and $B$.

@@

As there can be many interpolants for an ideal-pair $(J_A, J_B)$, 
the following questions should also be investigated in the future:
\bi
\item Find the minimal interpolant: i.e. find the interpolant $F_P$
  such that $V(J_P)$ is the smallest variety larger than $V(J_A)$ such
  that $V(J_P) \cap V(J_B) = \emptyset$.
\item Analogously, find the maximal interpolant. 
\item Over finite fields, the variety of an elimination ideal is
  exactly equal to the projection of the variety on the un-eliminated
  variables. Consider Fig. \ref{fig:projection}, where variety of the
  ideals $J_A, J_B$ are respectively projected on the common variables
  $X_C = \{a, c\}$. Then, does computing $F_{P1}$ (resp. $F_{P2}$) 
  deliver the minimal (resp. maximal) interpolant?
\ei

>>>>

\section{Future Work}
In this section, we highlight some research problems that deserve further study.
\subsection{Multivariate Polynomial Ideal based FSM Traversal}
In Chapter \ref{ch:reacha}, we always use a single word-level variable $T$ to denote the
next state. However, in some situations we need to keep recording the relations between $T$ and
inputs, {\it i.e.} the reached states contain multivariate polynomials in $T,S$ and PI $x$. 
While the elimination and set union/intersection are compatible with multiple NS variables,
the set complement requires an extension of Theorem \ref{thm:quotient} on ideals with 
multivariate polynomial generators. We conjecture as follows:

@@

\subsection{Use of the $F_4$ Algorithm and ZDDs to Accelerate GB Reduction}
In Chapters \ref{ch:reacha} and \ref{ch:normal}, by using RATO we transform the GB-based
computation to that of a multivariate polynomial division. However, this division (reduction)
still incurs exponential complexity in the worst case. In a situation where division is to be performed modulo
a chain of OR gates, the size of remainder polynomial will explode. For example, a chain of OR gates 
can be written as the Boolean function 
\begin{equation}
\label{eqn:chainOR}
f = ((a\lor b) \lor c) \lor d
\end{equation}
which equals to the following polynomial function in $\F_2$:
$$f = abcd+abc+abd+ab+acd+ac+ad+a+bcd+bc+bd+b+cd+c+d$$
Notice, $f$ contains $2^4-1 = 15$ terms, which is exponential in the number of variables.
The size explosion is a major factor affecting the efficiency of polynomial division.

@@

\begin{Definition}
(From \cite{mcmillan2003interpolation}) Let $A$ and $B$ be Boolean
  formulas given as sets of clauses such that $A \wedge B$ is
  unsatisfiable (UNSAT). Then there exists a formula $P$ such that: 
1) $A$ implies $P$ (or $A \subseteq P$); ~2) $P \wedge B$ is UNSAT; ~3)
$P$ refers to only the common variables of $A$ and $B$. The formula
$P$ represents an {\bf interpolant} of $A$ and $B$.

@@

As there can be many interpolants for an ideal-pair $(J_A, J_B)$, 
the following questions should also be investigated in the future:
\bi
\item Find the minimal interpolant: {\it i.e.} find the interpolant $F_P$
  such that $V(J_P)$ is the smallest variety larger than $V(J_A)$ such
  that $V(J_P) \cap V(J_B) = \emptyset$.
\item Analogously, find the maximal interpolant. 
\item Over finite fields, the variety of an elimination ideal is
  exactly equal to the projection of the variety on the remaining
  variables. Consider Figure \ref{fig:projection}, where variety of the
  ideals $J_A, J_B$ are respectively projected on the common variables
  $X_C = \{a, c\}$. Then, does computing $F_{P1}$ (resp. $F_{P2}$) 
  deliver the minimal (resp. maximal) interpolant?
\ei

### 2016-12-11 dissertation/intro.tex
dissertation v3:milestone

\section{Hardware Design and Verification Overview}
During the last decades, the level of integration in modern VLSI systems is becoming higher and higher because of the Moore's law.
As a result, an entire system with billions of transistors can be built upon a single chip.
The design process also evolves from manual design with little validation, to 
a formal 3-step procudure which requires collaboration of teams with large number of 
engineers. The 3 major steps are: 1) Design, which is to specify and enter the design intent;
2) Implement, which is to refine the design through various abstraction levels with the assistance of Computer-Aided-Design (CAD)
tools; 3) Verify, which is to verify the correctness of design and implementation.

Nowadays the verification step is usually completed by a team that specializes on test, verification and validation of 
circuits. This step is also automated as an indispensable part of the CAD flow, when circuit synthesis is performed. 
Figure \ref{fig:designflow} shows the typical synthesis flow, which covers procedures starting from the 
register-transfer-level (RTL) description (using hardware design languages, i.e. HDL) to  the 
physical design on silicon (depicted by the layout). The objective of verification in synthesis is 
to ensure the implementation is consistent with the original design intent. Verification is 
an important quality control measure before sending design layout to the VLSI foundaries.
Considering the high cost of fabrication, faults and errors in the design will bring considerable 
waste of funds for the designers. On the other hand, all aspects of the society increasingly depend on 
the stability and accuracy of digital VLSI circuits; even small flaws or short-time failures can cause 
huge loss, especially in medical applications, military facilities and financial systems.
Therefore, it is of utmost importance to verify the correctness of VLSI designs.

One way to perform verification is by {\it simulation}. It is defined as the collage of all circuit validation 
methods which apply stimulus on the inputs of circuit model and verify correctness of the outputs.
However, simulation is not a complete solution to circuit verification problems. In modern designs with 
large number of logic components and complicated architecures, it is impractical to simulate all possible 
test vectors. Usually only test vectors that correspond to typical failures are selected in simulation, which 
cannot cover unexpected failure patterns caused by special inputs. The notorious Intel FDIV bug \cite{nicely:FDIV}
is a good example where simulation failed. Failure occurred with input assignments which were rarely used in most divisions. Because of the limitation of simulation,  
test engineers from Intel failed to detect the bug,  which brought about $\$475$ million dollors recalling bill
for the company. Thus,  new methods that can guarantee the correctness of the design are necessary to be explored.

@@

\section{Formal Verification: Property and Equilavence Checking}

@@

\item \emph{Model checking} \cite{modelcheck:99} is a technique 
for verifying if the specification properties are violated in finite-state systems. In the circuit verification 
domain, both the specification and the circuit implementation are modeled as a system of 
logic formulas. The finite-state system is then traversed to check if the 
properties are violated. If violation occurs, 
a counter-example is then generated as a transition firing path that corresponds to the
false behavior in the design. 
Modern model checking techniques use the error-trace to automatically refine
the system and perform further checkings.
\end{enumerate}

@@

There are three major
equivalence checking techniques: graph-based,
satisfiability-based (SAT-based) and induction-based.
\begin{enumerate}[{1)}]
\item \emph{Graph-based} techniques compare two circuit implementations 
by representing them using canonical graphs. 
The earliest invented canonical graph is the \emph{Binary Decision Diagram} (BDD) \cite{BRYA86}.
Many variants branch out from BDDs; some widely used variants include 
ZDD \cite{minato1993zero}, BMD \cite{bmd}, FDD \cite{okfdd}, etc. The comparison algorithms can 
determine whether the two graphs are isomorphic. The canonity of the graph representation guarantees that
the graphs correspond to the two circuits will be 
equivalent if and only if the circuits implement the same function.
\item \emph{Satisfiability} (SAT) techniques utilize the satisfiability theory.
In circuit equivalence checking, a miter of the two circuits is created.
A \emph{miter} is a combination of the two circuits with one bit-level output, which 
gives output ``1" only when the outputs of the circuits differ with 
the same inputs, {\it e.g. }inputs $a,b,c$ shown in Figure \ref{fig:miter}. 
A SAT solver \cite{csat,mishchenko2006improvements} is then employed to simplify the problem 
and find a satisfying assignment to the inputs for which the 
miter output is ``1". If such an assignment exists, this solution acts as a 
counter-example to equivalence; otherwise the circuits
are functionally equivalent.
\item \emph{Induction-based} techniques are developed and applied to verify the 
equivalence between sequential circuits, which is called the {\it sequential equivalence checking}
(SEC) problem. A miter model can also be built with two sequential circuits. Through the 
miter model, SEC problem is transformed into a sequential backward justification problem.
Equivalence of states and transitions between states can be proved using induction-based 
proof and fix-point calculation \cite{bjesse2000sat,stoffel1997record}.
\end{enumerate}

@@

While the above techniques have made significant strides in sequential
verification, numerous practical instances remain unsolved. One issue
with all of the above techniques is that they mostly use bit-level
constraints to model the transition relations and sets of 
states. Often,
the designs are expressed at the level of bit-vector words
(e.g. Matlab code, Verilog), and these word-level abstractions are
rarely exploited in verification. The problem is further exacerbated
when there are arithmetic operators on word-level operands embedded in
the control logic. While attempts have been made towards word-level
predicate abstraction \cite{jain2005word,mcmillan:cav06,mcmillan2010lazy}, 
{\it using a purely word-level representation
  of the state-space, the properties and their abstractions have not
  been fully explored as another dimension in improving sequential
  verification.}

@@

In this dissertation we represent
the FSMs -- the transition relations -- by means of a set of
multi-variate polynomials with coefficients from the finite (Galois)
field $\Fkk$ of $2^k$ elements, i.e. polynomials in the ring
$\Fkk[x_1,\dots,x_d]$. Each state of a FSM is identified with a
Boolean assignment to a set of $k$-bit state register variables
$S=\{s_0,\dots,s_{k-1}\}$. Therefore, we can consider each ($k$-bit)
state as a word-level element $S$ of the finite field
$\Fkk$. Algorithms can directly operate on polynomials in word-level
variable $S$.

Boolean functions with $k$-bit inputs and $k$-bit outputs 
$f: \B^k \rightarrow \B^k,\B = \{0, 1\}$ can be construed as functions
$f: \Fkk \rightarrow \Fkk$. It is well-known that over the finite
field ($\Fq$) of  $q$ elements, every function $f: \Fq
\rightarrow \Fq$ is a polynomial function \cite{ff:1997}. Moreover,
there exists a unique canonical polynomial $\Func$ that describes $f$.
This implies that one can derive a canonical, polynomial
  abstraction of the function as $Z = \Func(A)$ where $Z, A$ are
word-level symbols representing $k$-bit operands. The concept also
generalizes to functions with different input/output bit-vector sizes,
i.e. functions of the type $f: \B^n \rightarrow \B^m$, modeled as
polynomials over $f:{\mathbb{F}}_{2^k} \rightarrow
{\mathbb{F}}_{2^k}$, where $k=LCM(n,m)$ \cite{ff:1997}.  
{\it This implies that the FSM's transition relations can be
represented as polynomial functions (ideals) in $\Fkk$, and values of
state variables can be represented as solutions to these polynomials}
(variety of the ideal). Subsequently, the ideal-variety correspondences
in algebraic geometry can be applied to implement symbolic reasoning
about state reachability. 
% Moreover, as ${\mathbb{F}}_2 \subset \Fkk$,
% our model provides a single, unified and bit-precise representation
% for both bit-level (${\mathbb{F}}_2$) and word-level ($\Fkk$)
% constraints.

>>>>

\section{Hardware Design and Verification Overview}
During the last decades, the level of integration in modern VLSI systems is becoming higher and higher because of the Moore's law.
As a result, an entire system with billions of transistors can be built upon a single chip.
The design process also evolves from manual design with little validation, to 
a formal 3-step procedure which requires collaboration of teams with large number of 
engineers. The 3 major steps are: 1) Design, which is to specify and enter the design intent;
2) Implement, which is to refine the design through various abstraction levels with the assistance of Computer-Aided-Design (CAD)
tools; 3) Verify, which is to verify the correctness of design and implementation.

Nowadays the verification step is usually completed by a team that specializes on test, verification and validation of 
circuits. This step is also automated as an indispensable part of the CAD flow, when circuit synthesis is performed. 
Figure \ref{fig:designflow} shows the typical synthesis flow, which covers procedures starting from the 
register-transfer-level (RTL) description (using hardware design languages, {\it i.e.} HDL) to  the 
physical design on silicon (depicted by the layout). The objective of verification in synthesis is 
to ensure the implementation is consistent with the original design intent. Verification is 
an important quality control measure before sending design layout to the VLSI foundries.
Considering the high cost of fabrication, faults and errors in the design will bring considerable 
waste of funds for the designers. On the other hand, all aspects of the society increasingly depend on 
the stability and accuracy of digital VLSI circuits; even small flaws or short-time failures can cause 
huge loss, especially in medical applications, military facilities and financial systems.
Therefore, it is of utmost importance to verify the correctness of VLSI designs.

One way to perform verification is by {\it simulation}. It is defined as the collage of all circuit validation 
methods which apply stimulus on the inputs of circuit model and verify correctness of the outputs.
However, simulation is not a complete solution to circuit verification problems. In modern designs with 
large number of logic components and complicated architectures, it is impractical to simulate all possible 
test vectors. Usually only test vectors that correspond to typical failures are selected in simulation, which 
cannot cover unexpected failure patterns caused by special inputs. The notorious Intel FDIV bug \cite{nicely:FDIV}
is a good example where simulation failed. Failure occurred with input assignments which were rarely used in most divisions. Because of the limitation of simulation,  
test engineers from Intel failed to detect the bug,  which brought about $\$475$ million dollars recalling bill
for the company. Thus,  new methods that can guarantee the correctness of the design are necessary to be explored.

@@

\section{Formal Verification: Property and Equivalence Checking}

@@

\item \emph{Model checking} \cite{modelcheck:99} is a technique 
for verifying if the specification properties are violated in finite-state systems. In the circuit verification 
domain, both the specification and the circuit implementation are modeled as a system of 
logic formulas. The finite-state system is then traversed to check if the 
properties are violated. If violation occurs, 
a counter-example is then generated as a transition firing path that corresponds to the
false behavior in the design. 
Modern model checking techniques use the error-trace to automatically refine
the system and perform further checking.
\end{enumerate}

@@

There are three major
equivalence checking techniques: graph-based,
satisfiability-based (SAT-based) and induction-based.
\begin{enumerate}[{1)}]
\item \emph{Graph-based} techniques compare two circuit implementations 
by representing them using canonical graphs. 
The earliest invented canonical graph is the \emph{Binary Decision Diagram} (BDD) \cite{BRYA86}.
Many variants branch out from BDDs; some widely used variants include 
ZDD \cite{minato1993zero}, BMD \cite{bmd}, FDD \cite{okfdd}, {\it etc.} The comparison algorithms can 
determine whether the two graphs are isomorphic. The canonicity of the graph representation guarantees that
the graphs correspond to the two circuits will be 
equivalent if and only if the circuits implement the same function.
\item \emph{Satisfiability} (SAT) techniques utilize the satisfiability theory.
In circuit equivalence checking, a miter of the two circuits is created.
A \emph{miter} is a combination of the two circuits with one bit-level output, which 
gives output ``1" only when the outputs of the circuits differ with 
the same inputs, {\it e.g. }inputs $a,b,c$ shown in Figure \ref{fig:miter}. 
A SAT solver \cite{csat,mishchenko2006improvements} is then employed to simplify the problem 
and find a satisfying assignment to the inputs for which the 
miter output is ``1". If such an assignment exists, this solution acts as a 
counter-example to equivalence; otherwise the circuits
are functionally equivalent.
\item \emph{Induction-based} techniques are developed and applied to verify the 
equivalence between sequential circuits, which is called the {\it sequential equivalence checking}
(SEC) problem. A miter model can also be built with two sequential circuits. Through the 
miter model, SEC problem is transformed into a sequential backward justification problem.
Equivalence of states and transitions between states can be proved using induction-based 
proof and fix-point calculation \cite{bjesse2000sat,stoffel1997record}.
\end{enumerate}

@@

While the above techniques have made significant strides in sequential
verification, numerous practical instances remain unsolved. One issue
with all of the above techniques is that they mostly use bit-level
constraints to model the transition relations and sets of 
states. Often,
the designs are expressed at the level of bit-vector words
({\it e.g.} Matlab code, Verilog), and these word-level abstractions are
rarely exploited in verification. The problem is further exacerbated
when there are arithmetic operators on word-level operands embedded in
the control logic. While attempts have been made towards word-level
predicate abstraction \cite{jain2005word,mcmillan:cav06,mcmillan2010lazy}, 
{\it using a purely word-level representation
  of the state-space, the properties and their abstractions have not
  been fully explored as another dimension in improving sequential
  verification.}

@@

In this dissertation we represent
the FSMs -- the transition relations -- by means of a set of
multi-variate polynomials with coefficients from the finite (Galois)
field $\Fkk$ of $2^k$ elements, {\it i.e.} polynomials in the ring
$\Fkk[x_1,\dots,x_d]$. Each state of a FSM is identified with a
Boolean assignment to a set of $k$-bit state register variables
$S=\{s_0,\dots,s_{k-1}\}$. Therefore, we can consider each ($k$-bit)
state as a word-level element $S$ of the finite field
$\Fkk$. Algorithms can directly operate on polynomials in word-level
variable $S$.

Boolean functions with $k$-bit inputs and $k$-bit outputs 
$f: \B^k \rightarrow \B^k,\B = \{0, 1\}$ can be construed as functions
$f: \Fkk \rightarrow \Fkk$. It is well-known that over the finite
field ($\Fq$) of  $q$ elements, every function $f: \Fq
\rightarrow \Fq$ is a polynomial function \cite{ff:1997}. Moreover,
there exists a unique canonical polynomial $\Func$ that describes $f$.
This implies that one can derive a canonical, polynomial
  abstraction of the function as $Z = \Func(A)$ where $Z, A$ are
word-level symbols representing $k$-bit operands. The concept also
generalizes to functions with different input/output bit-vector sizes,
{\it i.e.} functions of the type $f: \B^n \rightarrow \B^m$, modeled as
polynomials over $f:{\mathbb{F}}_{2^k} \rightarrow
{\mathbb{F}}_{2^k}$, where $k=LCM(n,m)$ \cite{ff:1997}.  
{\it This implies that the FSM's transition relations can be
represented as polynomial functions (ideals) in $\Fkk$, and values of
state variables can be represented as solutions to these polynomials}
(variety of the ideal). Subsequently, the ideal-variety correspondences
in algebraic geometry can be applied to implement symbolic reasoning
about state reachability. 
% Moreover, as ${\mathbb{F}}_2 \subset \Fkk$,
% our model provides a single, unified and bit-precise representation
% for both bit-level (${\mathbb{F}}_2$) and word-level ($\Fkk$)
% constraints.
